---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "70%"
)
```

# Google Location data during the Covid-19 period

Archive of data extracted from Google's [Community Mobility
Reports](https://www.google.com/covid19/mobility/).  All countries are included.

## Data Quality

The onus is on you to check against the originnal PDF files, but this should be
okay to use. Previous problems have been fixed.  It has been checked against
similar work by the [Office for National Statistics Data Science
Campus](https://github.com/datasciencecampus/mobility-report-data-extractor).

## Countries by category

Illustration of the data only.  Google recommends against comparing changes
between countries or regions.

> Location accuracy and the understanding of categorized places varies from
> region to region, so we don’t recommend using this data to compare changes
> between countries, or between regions with different characteristics (e.g.
> rural versus urban areas).

```{r plot-countries-by-category, echo = FALSE, message = FALSE}
library(tidyverse)
library(gghighlight)
library(plotly)

one_percent <- partial(scales::percent, accuracy = 1)

df <- read_tsv("./2020-03-29.tsv", col_types = "ciccDciiccdidD")

df %>%
  filter(type == "country") %>%
  ggplot(aes(date, trend, group = interaction(group, country_code))) +
  geom_line(alpha = .1) +
  scale_y_continuous(labels = one_percent) +
  coord_cartesian(ylim = c(-1, 1)) +
  facet_wrap(vars(category), scales = "free_y") +
  labs(x = "", y = "Change from baseline",
       title = "Google Community Mobility Reports per Country",
       subtitle = "Comparison between countries is not recommended")
```

## Data download

For now, download a [dated
file](https://raw.githubusercontent.com/nacnudus/google-location-coronavirus/master/2020-03-29.tsv). It is tab-separated.

## Method

Based on similar work by the [Office for National Statistics Data Science
Campus](https://github.com/datasciencecampus/mobility-report-data-extractor).

1. Convert the PDF files to SVG format, and extract the trend lines.
1. Extract text from the PDF.
1. Pair up the text with the trends.

The differences are:

1. All countries are included.
1. Using R, instead of Python
1. Scripting pdf->svg file conversion with
   [`pdf2svg`](https://github.com/dawbarton/pdf2svg), rather than doing it
   manually.

